Calls vs IMD

### 2022-02-01 output/calls_vs_imd.Rmd
working on IMD report

weekly_count_by_lsoa <- cheshire_calls %>% 
   mutate(inc_wk = yearweek(incident_date_time)) %>%   
   group_by(lsoa, inc_wk) %>% count() %>% 
  left_join(lsoa_filler, .) %>%
    mutate(n = replace_na(n, 0)) %>% 
    left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
  mutate(n = replace_na(n, 0)) %>% 
  group_by(index_of_multiple_deprivation_imd_decile, inc_wk) %>% 
  summarise(avg_weekly_call = mean(n, na.rm = T), 
            n_per_lsoa = n/n())
# 
# ggplot(weekly_count_by_lsoa, aes(x = inc_wk, y = avg_weekly_call, colour = as.factor(index_of_multiple_deprivation_imd_decile))) +
#   geom_point() + 
#   geom_line()

@@

>>>>

weekly_count_by_lsoa <- cheshire_calls %>% 
   mutate(inc_wk = as_date(yearweek(incident_date_time))) %>%   
   group_by(lsoa, inc_wk) %>% count() %>% 
  left_join(lsoa_filler, .) %>%
    mutate(n = replace_na(n, 0)) %>% 
    left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) # check why NAs

firstweek <- min(weekly_count_by_lsoa$inc_wk)
lastweek <- max(weekly_count_by_lsoa$inc_wk)

weekly_count_by_lsoa <- weekly_count_by_lsoa %>% 
  filter(inc_wk > firstweek & inc_wk < lastweek)

num_lsoa_per_decile <- weekly_count_by_lsoa %>% 
  select(lsoa, index_of_multiple_deprivation_imd_decile) %>% 
  distinct() %>% 
  group_by(index_of_multiple_deprivation_imd_decile) %>% 
  count() %>% 
  rename(num_lsoas = n)

thing <- weekly_count_by_lsoa %>% 
  left_join(., num_lsoa_per_decile, by = c("index_of_multiple_deprivation_imd_decile" = "index_of_multiple_deprivation_imd_decile")) %>% 
  select(inc_wk, n, index_of_multiple_deprivation_imd_decile, num_lsoas)  %>% 
  group_by(inc_wk, index_of_multiple_deprivation_imd_decile, num_lsoas) %>%
  summarise(n = sum(n)) %>%
  mutate(calls_per_lsoa = n/num_lsoas) %>% 
  group_by(inc_wk, index_of_multiple_deprivation_imd_decile) %>%
  summarise(calls_per_lsoa = calls_per_lsoa) %>% 
    mutate(percentage = calls_per_lsoa / sum(calls_per_lsoa))

# Plot
ggplot(thing, aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
    geom_area(alpha= 1 , size=0.001, colour="black") +
  # First UK case
  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
  # First UK lockdown begins
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
  # First UK lockdown ends
  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(type = "qual", palette = "Paired") + 
  labs(
    title = "Proportion of Calls from different IMD deciles",
    x = NULL,
    y = "Proportion",
    fill = "IMD decile"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))

@@

zoom

# Plot
ggplot(thing %>% filter(inc_wk > as.Date("2019-10-10")), 
       aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
    geom_area(alpha= 1 , size=0.001, colour="black") +
  # First UK case
  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
  # First UK lockdown begins
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
  # First UK lockdown ends
  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(type = "qual", palette = "Paired") + 
  labs(
    title = "Proportion of Calls from different IMD deciles",
    x = NULL,
    y = "Proportion",
    fill = "IMD decile"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))

## Breakdown by call type

imd_area_plot <- function(inc_type) {

# Plot
ggplot(thing %>% filter(inc_wk > as.Date("2019-10-10")), 
       aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
    geom_area(alpha= 1 , size=0.001, colour="black") +
  # First UK case
  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
  # First UK lockdown begins
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
  # First UK lockdown ends
  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(type = "qual", palette = "Paired") + 
  labs(
    title = "Proportion of Calls from different IMD deciles",
    x = NULL,
    y = "Proportion",
    fill = "IMD decile"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))
